RNA-seq from 4 cell populations

### 2021-08-02 deconvolution/fans4/molec_profiling.Rmd
bug fix

```{r Disease.analysis}
df_disease = lapply(levels(info$CellType), function(CT){

@@

  tabl = topTable( fitDisease, coef = key, number=Inf)

  data.frame(CellType = CT, key, count = sum(tabl$adj.P.Val < 0.05), pi1 = 1 - qvalue(tabl$P.Value)$pi0)
  })
df_disease = do.call(rbind, df_disease)

kable(df_disease, digits=2, row.names=FALSE) %>% kable_styling(bootstrap_options = "striped", full_width = FALSE)
```

>>>>

```{r Disease.analysis.corr}
df_disease_de = lapply(levels(info$CellType), function(CT){

@@

  tabl = topTable( fitDisease, coef = key, number=Inf)
  tabl$CellType = CT
  tabl$ensID = rownames(tabl)
  tabl
  })
df_disease_de = data.table(do.call(rbind, df_disease_de))

df_disease_de[,data.frame(count = sum(adj.P.Val < 0.05), pi1 = 1 - qvalue(P.Value)$pi0), by="CellType"] %>% kable(digits=2, row.names=FALSE) %>% kable_styling(bootstrap_options = "striped", full_width = FALSE)

  df_tstat = merge(df_disease_de[CellType==CT1,], df_disease_de[CellType==CT2,], by="ensID")

  r = with(df_tstat, cor(z.std.x, z.std.y, method="spearman"))

  data.frame(CT1, CT2, corr = r)
})
tabList = do.call(rbind, tabList)

tabList %>% kable(digits=2, row.names=FALSE) %>% kable_styling(bootstrap_options = "striped", full_width = FALSE)

ggplot(tabList, aes(CT1, CT2, fill=corr)) + geom_tile() + theme_bw(15) + theme(aspect.ratio=1, plot.title = element_text(hjust = 0.5), panel.grid.major = element_blank(), panel.grid.minor = element_blank()) + scale_fill_gradient(name = quote(pi[1]), low="white", high="red", limits=c(0, 1)) + geom_text(aes(label=format(corr, digits=3))) + xlab('') + ylab('') + ggtitle("Correlation between t-statistics")

C = matrix(1, 4,4)
rownames(C) = levels(info$CellType)
colnames(C) = levels(info$CellType)
tabList$CT1 = factor(tabList$CT1, levels(info$CellType))
tabList$CT2 = factor(tabList$CT2, levels(info$CellType))

for(i in 1:nrow(tabList)){
  C[tabList$CT1[i],tabList$CT2[i]] = tabList$corr[i]
  C[tabList$CT2[i],tabList$CT1[i]] = tabList$corr[i]
}

plot(hclust(as.dist(1-C)))
```
